Crawler and Inverted Index in Java

### 2023-11-05 latexJava/paperJava.tex
added datamart to paperJava.tex

>>>>

\subsection{Datamart}

The Datamart module handles the storage and management of the inverted index. It defines methods for indexing keywords, retrieving documents associated with a keyword, and obtaining a list of all available documents in the index. Two implementations are provided: a SQL-based Datamart using SQLite and a File-based Datamart using file storage.
\begin{itemize}

\item 
The SQL-based Datamart in \texttt{SqlDatamart} module stores the inverted index using a SQL database, associating keywords with document lists.

\item 
The File-based Datamart in \texttt{FileDatamart} module employs file storage to maintain the inverted index, where each keyword corresponds to a file containing document IDs. 
\end{itemize}
The Datamart module provides a reliable solution for the storage and retrieval of the inverted index. The choice between provided implementations depends on project requirements and scale.
File-Based approach is suitable for smaller-scale projects where a full database system might be unnecessary, offering flexibility and efficiency in data storage.
